Market Simulator

### 2020-07-23 analysis/05_market_simulator.Rmd
small updates getting sidebar to work

#Levels (This is a guess):            Means:
#   1. Amnesty International          0.805
#   2. Greenpeace                     0.923
#   3. Oxfam                          0.620
#   4. Red Cross                      1.820
#   5. Environment                   -0.444
#   6. Human Rights                  -0.164
#   7. Refugee Relief                -0.582
#   8. Financially Transparent        1.080
#   9. Accountable                    1.130
#   10. Small wealthy donars         -0.376
#   11. Government Grants            -0.252
#   12. Critized by Government       -0.663
#   13. Under Government Crackdown   -1.011

@@

@@

Inputs {.sidebar data-width=50}
-------------------------------------------------------

@@

``` {r echo=FALSE}

@@

Organization Utility
-------------------------------------
Amnesty International Expected Utility

>>>>

#Levels (This is a guess):            Means:
#   1. Amnesty International          0.805
#   2. Greenpeace                     0.923
#   3. Oxfam                          0.620
#   4. Red Cross                      1.820
#   5. Environment                   -0.444
#   6. Human Rights                  -0.164
#   7. Refugee Relief                -0.582
#   8. Financially Transparent        1.080
#   9. Accountable                    1.130
#   10. Small wealthy donors         -0.376
#   11. Government Grants            -0.252
#   12. Criticized by Government       -0.663
#   13. Under Government Crackdown   -1.011

@@

```{r functions}
#### This chunk can be used for writing function to calculate the utilities and what not

@@

Inputs {.sidebar}
-------------------------------------------------------

@@

@@

Organization Utility
-------------------------------------
## Amnesty International Expected Utility
